---
title: 'Arizona Groundwater research'
author: "[Angus Watters](https://anguswg-ucsb.github.io/)"
output:
  mikedown::ucsb:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---


```{r, message= FALSE, warning = FALSE, echo = FALSE}

library(tidyverse)
library(rmarkdown)     # You need this library to run this template.
library(mikedown)   
```



***

```{r, message= FALSE, warning = FALSE, echo = TRUE}
# Libraries
library(tidyverse)
library(sf)
library(USAboundaries)
library(ggthemes)
library(cowplot)
library(sp)
library(leaflet)
```

```{r, message= FALSE, warning = FALSE, echo = FALSE}
source("../docs/utils.R") 
```

<br>
<br>

# **Measurement threshold** *(1960 - 2000)*
A minimum threshold of 10 distinct measurements with at least 1 measurement every 5 years was applied to filter for only the regularly monitored wells. investigate regularly monitored wells 

***

<br>
<br>


```{r, message= FALSE, warning = FALSE, echo = FALSE}
source("../docs/az-usgs-dtw.R") 
source("../docs/az-state-dtw.R") 
```


```{r, message = FALSE, warning = FALSE, echo = TRUE}
# Data from USGS National Water Information System (NWIS)

# Arizona state shape (CRS = 5070)
az = us_states() %>% 
  filter(name == 'Arizona') %>% 
  st_transform(5070)

# add 'well #' for each unique well
usgs = az_nwis_unique_sites
usgs$wellid = paste("well", 1:nrow(usgs))

# remove wells located at same lat/long but have different well ID
usgs_spatial = usgs %>% 
  st_as_sf(coords = c('long_nad83', 'lat_nad83'), crs = 4269) %>% 
  st_transform(5070) %>%
  as_Spatial() %>% 
  remove.duplicates() %>% 
  st_as_sf() %>% 
  group_by(wellid)

# match 'well #' from spatial data frame to corresponding well in time series data frame
usgs_time = az_nwis_all %>% 
  group_by(site_id) 
usgs_time = left_join(usgs_time, select(usgs, site_id, wellid), by = "site_id") 
usgs_time = usgs_time %>% filter(wellid %in% usgs_spatial$wellid)

# FILTER BY THRESHOLD - at least 10 measurements and at least 1 measurement every 5 years
thresh = usgs_time %>% 
  group_by(wellid) %>% 
  filter(measurement_dist >= 10) %>% 
  mutate(measure_period = year - lag(year)) %>% 
  filter(any(measure_period > 5))
usgs_time = usgs_time %>% filter(!wellid %in% thresh$wellid, measurement_dist >= 10) %>% 
  mutate(measure_period = year - lag(year))
usgs_spatial = usgs_spatial %>% 
  filter(!wellid %in% thresh$wellid) %>% 
  filter(measurement_dist >= 10)


# Data from Arizona Department of Water Resources (ADWR)

# add 'well #' for each unique well
state = adwr_unique_sites %>%
  filter(date > 1960-01-01, date < as.Date.character('2000-01-01'))
state$wellid = paste("well", 1:nrow(state))

# remove wells located at same lat/long but have different well ID
state_spatial = state %>%
  st_as_sf(coords = c('long_nad83', 'lat_nad83'), crs = 4269) %>%
  st_transform(5070) %>%
  as_Spatial() %>%
  remove.duplicates() %>%
  st_as_sf() %>%
  group_by(site_id)

# match 'well #' from spatial data frame to corresponding well in time series data frame
state_time = adwr_all %>%
  group_by(site_id)
state_time = left_join(state_time, select(state, site_id, wellid), by = "site_id")
state_time = state_time %>% filter(wellid %in% state_spatial$wellid)

# FILTER BY THRESHOLD - at least 10 measurements and at least 1 measurement every 5 years
thresh_state = state_time %>%
  group_by(wellid) %>%
  filter(measurement_dist >= 10) %>%
  mutate(measure_period = year - lag(year)) %>%
  filter(any(measure_period > 5))
state_time = state_time %>% filter(!wellid %in% thresh_state$wellid, measurement_dist >= 10) %>%
  mutate(measure_period = year - lag(year))
state_spatial = state_spatial %>%
  filter(!wellid %in% thresh_state$wellid) %>%
  filter(measurement_dist >= 10)

```


```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
ama = read_sf('../data/Act_Man_Areas.shp') %>% 
  st_transform(5070) %>% 
  st_cast("MULTIPOLYGON")

ama2 = ama %>% st_transform(4326)

### AQUIFERS
aquifer = read_sf('../data/shps/us_aquifers.shp') %>% 
  st_transform(5070) %>% 
  st_cast("MULTIPOLYGON")

aquifer2 = aquifer %>% st_transform(4326)

box = az %>% st_transform(4326) %>% 
  st_bbox() %>% 
  st_as_sfc()
temp = st_intersects(aquifer2, box)

aquifer2 = aquifer2[which(lengths(temp) != 0), ]

x = usgs_spatial %>% st_transform(4326)


col1 = RColorBrewer::brewer.pal(9,"Blues")
col2 = RColorBrewer::brewer.pal(9,"YlOrRd")
col3 = RColorBrewer::brewer.pal(9,"YlGnBu")
col4 = RColorBrewer::brewer.pal(9,"Spectral")

pals1 = colorNumeric(col1, domain = x$dtw)
pals2 = colorNumeric(col2, domain = x$dtw)
pals3 = colorBin(col3, domain = 1:8)
pals4 = colorFactor(col4, domain = aquifer2$AQ_NAME)

a = dtw_range(x, 0, 100) %>% select(wellid, date, dtw, measurement_dist)
b = dtw_range(x, 100, 200) %>% select(wellid, date, dtw, measurement_dist)
c = dtw_range(x, 200, 300) %>% select(wellid, date, dtw, measurement_dist)
d = dtw_range(x, 300, 400) %>% select(wellid, date, dtw, measurement_dist)
e = dtw_range(x, 400, 500) %>% select(wellid, date, dtw, measurement_dist)
f = dtw_range(x, 500, 600) %>% select(wellid, date, dtw, measurement_dist)
g = dtw_range(x, 600, 700) %>% select(wellid, date, dtw, measurement_dist)
h = dtw_range(x, 700, 800) %>% select(wellid, date, dtw, measurement_dist)
i = dtw_range(x, 800, 900) %>% select(wellid, date, dtw, measurement_dist)
j = dtw_range(x, 900, 1500) %>% select(wellid, date, dtw, measurement_dist)

# State leaflet 
z = state_spatial %>% st_transform(4326)

aa = dtw_range(z, 0, 100) %>% select(wellid, date, dtw, measurement_dist)
bb = dtw_range(z, 100, 200) %>% select(wellid, date, dtw, measurement_dist)
cc = dtw_range(z, 200, 300) %>% select(wellid, date, dtw, measurement_dist)
dd = dtw_range(z, 300, 400) %>% select(wellid, date, dtw, measurement_dist)
ee = dtw_range(z, 400, 500) %>% select(wellid, date, dtw, measurement_dist)
ff = dtw_range(z, 500, 600) %>% select(wellid, date, dtw, measurement_dist)
gg = dtw_range(z, 600, 700) %>% select(wellid, date, dtw, measurement_dist)
hh = dtw_range(z, 700, 800) %>% select(wellid, date, dtw, measurement_dist)
ii = dtw_range(z, 800, 900) %>% select(wellid, date, dtw, measurement_dist)
jj = dtw_range(z, 900, 1500) %>% select(wellid, date, dtw, measurement_dist)






leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron, group = 'Tiles') %>% 
  addPolygons(data = ama2,
              fillColor  = ~pals3(OBJECTID), fillOpacity = 0.3,
              color = 'black',
              label = ~MAP_LABEL, group = 'AMA') %>%
  addPolygons(data = aquifer2, fillColor = ~pals4(AQ_NAME), fillOpacity = 0.3,
              color = 'black',
              label = ~AQ_NAME, group = 'Aquifer') %>%
  addCircleMarkers(data = a, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(a, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '0 - 100 ft') %>% 
  addCircleMarkers(data = b, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(b, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '100 - 200 ft') %>% 
  addCircleMarkers(data = c, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(c, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '200 - 300 ft') %>% 
  addCircleMarkers(data = d, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(d, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '300 - 400 ft') %>% 
  addCircleMarkers(data = e, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(e, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '400 - 500 ft') %>% 
  addCircleMarkers(data = f, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(f, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '500 - 600 ft') %>% 
  addCircleMarkers(data = g, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(g, feature.id = FALSE, 
                                               row.numbers = FALSE), group = '600 - 700 ft') %>% 
  addCircleMarkers(data = h, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(h, feature.id = FALSE,
                                               row.numbers = FALSE), group = '700 - 800 ft') %>%
  addCircleMarkers(data = i, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(i, feature.id = FALSE,
                                               row.numbers = FALSE), group = '800 - 900 ft') %>%
  addCircleMarkers(data = j, #clusterOptions = markerClusterOptions(interactive()),
                   color = ~pals2(dtw), fillOpacity = .8,
                   stroke = FALSE,
                   popup = leafpop::popupTable(j, feature.id = FALSE,
                                               row.numbers = FALSE), group = '900 > ft') %>%
  addCircleMarkers(data = aa, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1, fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(aa, feature.id = FALSE,
                                               row.numbers = FALSE), group = '0 - 100 ft') %>%
  addCircleMarkers(data = bb, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1,
                   fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(bb, feature.id = FALSE,
                                               row.numbers = FALSE), group = '100 - 200 ft') %>%
  addCircleMarkers(data = cc, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1,
                   fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(cc, feature.id = FALSE,
                                               row.numbers = FALSE), group = '200 - 300 ft') %>%
  addCircleMarkers(data = dd, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1, fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(dd, feature.id = FALSE,
                                               row.numbers = FALSE), group = '300 - 400 ft') %>%
  addCircleMarkers(data = ee, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1, fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(ee, feature.id = FALSE,
                                               row.numbers = FALSE), group = '400 - 500 ft') %>%
  addCircleMarkers(data = ff, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1, fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(ff, feature.id = FALSE,
                                               row.numbers = FALSE), group = '500 - 600 ft') %>%
  addCircleMarkers(data = gg, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1, fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(gg, feature.id = FALSE,
                                               row.numbers = FALSE), group = '600 - 700 ft') %>%
  addCircleMarkers(data = ii, #clusterOptions = markerClusterOptions(interactive()),
                   color = 'black', fillColor = ~pals2(dtw), opacity = 1, fillOpacity = .8,
                   stroke = TRUE,
                   popup = leafpop::popupTable(ii, feature.id = FALSE,
                                               row.numbers = FALSE), group = '800 - 900 ft') %>%
  addLayersControl(overlayGroups = c('0 - 100 ft', '100 - 200 ft', '200 - 300 ft',
                                     '300 - 400 ft', '400 - 500 ft',
                                     '500 - 600 ft', '600 - 700 ft',
                                     '700 - 800 ft', '800 - 900 ft', '900 > ft', 'AMA', 'Aquifer'),
                   baseGroups = c("Tiles"))
```

***

<br>
<br>
<br>
<br>



# **Wells deeper than 500ft**

***

<br>
<br>
<br>

## **500 - 1000ft** 

***

<br>

```{r, message= FALSE, warning = FALSE, echo=FALSE, out.width = "100%"}
multi_well_plot(usgs_spatial, usgs_time, 500, 1000)
```

<br>
<br>
<br>

***

## **500 - 600ft**

***

I decided to include these increments of 100ft as it is visually easier to track individual wells

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
multi_well_plot(usgs_spatial, usgs_time, 500, 600)
```

<br>
<br>
<br>

***

## **600 - 700ft**

***

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
multi_well_plot(usgs_spatial, usgs_time, 600, 700)
```

<br>
<br>
<br>

## **Wells with over 50 measurements**

***

<br>
<br>
<br>


### **Phoenix AMA**

***

<br>
<br>
<br>

### **Well 5284**

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 5284)
```

<br>
<br>
<br>

### **Well 5324**

***

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 5324)
```

<br>
<br>
<br>



### **Harquahala AMA**

***

<br>
<br>

### **Well 292**

***

<br>
```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 292)
```

<br>
<br>
<br>

### **Well 504** 

***

Located just north of Harquahala AMA boundary

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 504)
```

<br>
<br>
<br>

***

### **Kingman**

***

<br>
<br>

### **Well 1139**

***

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1139)
```

<br>
<br>
<br>

***

### **Outside Tuscan AMA**

***

<br>
<br>

### **Well 575**

***

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 575)
```

<br>
<br>
<br>

# **Wells deeper than 1000ft**

***

<br>
<br>

## **Flagstaff**

<br>

### **Well 1133**

***

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1133)
```



<br>
<br>
<br>

### **Well 1215**

***

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1215)
```

***

<br>
<br>
<br>

### **Well 3450** 

***

Well 3450 was monitored continuously since ~1965
```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 3450)
```

***

<br>
<br>
<br>

### **Well 1242**

***

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1242)
```

***

<br>
<br>
<br>

### **Well 1226**

***

Wells 1226 & 2710 had measurements recorded only for a couple years in the late 1990s

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1226)
```

***

<br>
<br>
<br>

### **Well 2710**

***

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 2710)
```

<br>
<br>
<br>
<br>

## **Between Flagstaff and Kingman**


***

<br>
<br>

### **Well 5155**

***

Northwest of Flagstaff and northeast of Kingman

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 5155)
```

<br>
<br>
<br>

## **Northeast of Flagstaff**

***

### **Well 1669**

***

shows a continual decline in DTW from ~1975 - 2000

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1669)
```


<br>
<br>
<br>

### **Well 1411**

***

Well 1411 is nearby to well 1669 and shows the same trend as 1669, 1411 has a max depth of 830 ft, just under 1000ft marker

<br>

```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
plot_well(usgs_time, 1411)
```




<br>
<br>
<br>

# **Arizona Department of Water Resources (ADWR)**

***

<br>
<br>

Using the same threshold applied to the USGS data of 10 distinct measurements with at least 1 measurement every 5 years, the total number of State monitored wells was significantly reduced.

<br>
<br>
<br>

### **300 - 400 ft** 
```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
three_four = state_time %>%  filter(wellid %in% dd$wellid)
multi_well_plot(state_spatial, three_four, 0, 1000)
```

<br>
<br>
<br>

### **400 - 500 ft** 
```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
four_five = state_time %>%  filter(wellid %in% ee$wellid)
multi_well_plot(state_spatial, four_five, 0, 1000)
```

<br>
<br>
<br>

### **500 - 600 ft**  
```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}
five_six = state_time %>%  filter(wellid %in% ff$wellid)
multi_well_plot(state_spatial, five_six, 0, 1000)
```

<br>
<br>
<br>

### **600 - 700 ft** 
```{r, message= FALSE, warning = FALSE, echo = FALSE, out.width = "100%"}

six_sev = state_time %>%  filter(wellid %in% gg$wellid)
multi_well_plot(state_spatial, six_sev, 0, 1000)
```

<br>
<br>
<br>



# **Functions**

***


```{r, message= FALSE, warning = FALSE, eval=FALSE, echo=TRUE}
# PLOTS A BUFFER AROUND SPECIFIED WELL AND LOCATES OTHER WELLS INSIDE THE BUFFER AREA
buffer_fun = function(df, well, buff, state) {
  buffer = st_buffer(df[well,], buff)
  near1 = st_intersection(df[,], buffer) %>% filter(measurement_dist >= 10)
  
  plot = ggplot() + 
    geom_sf(data = state) +
    geom_sf(data = buffer, fill = NA) + 
    geom_sf(data = near1, col = "red", size = .5) + 
    labs(caption = paste(nrow(near1), 'wells')) +
    theme_void() +
    theme(plot.caption = element_text(size = 22, face = "bold", hjust = 0.5))
  print(plot)
  return(near1)
}

# RETURNS DATAFRAME OF WELLS IN DTW RANGE (MIN - MAX)
dtw_range = function(df, min, max) {
  df = df %>% filter(dtw <= max, dtw >= min) %>% 
    mutate(sd = sd(dtw)) %>% 
    arrange(desc(date))
  return(df)
}


# PLOTS AN INDIVIDUAL WELL BY WELL ID (DTW TIME SERIES)
plot_well = function(df_time, id) {
  wells = df_time %>% filter(wellid == paste('well', id))
  plot = ggplot(data = wells, aes(x = date, y = dtw_ft)) +
    geom_line(aes(y = dtw_ft, col = wellid), size = 2) +
    scale_y_reverse() +
    labs(title = paste('Well', id),
         caption = paste('Min depth:', min(wells$dtw_ft), '\nMax depth:',
                          max(wells$dtw_ft), '\nNumber of measurements:',
                          wells$measurement_dist),
         x = 'Year',
         y = 'DTW (ft)') + 
    theme_bw() +
    theme(plot.title = element_text(face = 'bold',color = 'black', size = 18, hjust = 0.5),
          axis.text.x = element_text(color="black", size=14), 
          axis.text.y = element_text(color="black", size=14), 
          axis.title.x = element_text(face = 'bold', color="black", size=16), 
          axis.title.y = element_text(face = 'bold', color="black", size=16),
          plot.caption = element_text(face = 'bold', color = 'black', size = 14),
          panel.grid.major = element_line(colour = "#808080"),
          panel.grid.minor = element_line(colour = "#808080", size = 1),
          legend.position = 'none') 
  print(plot)
}

# PLOTS MULTIPLE WELLS IN DTW RANGE
multi_well_plot = function(df, df_time, min, max) {
  df = df %>% filter(dtw <= max, dtw >= min) %>% 
    arrange(desc(date))
  df_time = df_time %>% filter(wellid %in% df$wellid)
  plot1 = ggplot(data = df_time, aes(x = date, y = dtw_ft)) +
    geom_line(aes(y = dtw_ft, col = wellid), size = 1) +
    scale_y_reverse() +
    labs(x = 'Year',
         y = 'DTW (ft)') + 
    theme_bw() +
    theme(plot.title = element_text(face = 'bold',color = 'black', size = 18, hjust = 0.5), 
          axis.text.x = element_text(color="black", size=14), 
          axis.text.y = element_text(color="black", size=14), 
          axis.title.x = element_text(face="bold", color="black", size=16), 
          axis.title.y = element_text(face="bold", color="black", size=16), 
          panel.grid.major = element_line(colour = "#808080"),
          panel.grid.minor = element_line(colour = "#808080", size = 1),
          legend.position = 'none')
  print(plot1)
  return(df)
}


# PLOTS WELLS DTW WITHIN A SPECIFIED RANGE, COLOR GRADIENT BY DEPTH, RETURNS CORRESPONDING DATA FRAME
map_dtw = function(state, df, min, max) {
  df = df %>% filter(dtw <= max, dtw >= min) %>% 
    mutate(sd = sd(dtw)) %>% 
    arrange(dtw)
  plot1 = ggplot() + 
    geom_sf(data = state, size = 1, col = 'black') +
    geom_sf(data = df, aes(col = dtw), size = 1.5) + 
    theme_void() +
    theme(plot.title = element_text(face = "bold", color = "black", size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(face = 'bold', size = 12), 
          legend.title = element_text(color="black", size=14), 
          legend.text = element_text(color="black", size=14)) +
    scale_colour_gradient() +
    labs(title = paste('DTW', min, '-', max, 'ft'),
         fill = 'Number of wells', 
         col = 'Depth to Water (ft)')
  print(plot1)
  return(df)
}
```


























